R Notebook

### 2025-01-08 landscapemodels_margin.Rmd
update site with pairs plot for margin norm page

Change in ecosystem service is normalized by hectares of margin added so that the dependent variable is unit ES per area margin instead of per area watershed

>>>>

Change in ecosystem service is normalized by hectares of margin added so that the dependent variable is unit ES per area margin instead of per area watershed. I added total watershed area into the full models just to see if there is any association.

```{r correlation, echo = FALSE}

pairs.panels(wfs_lsm %>% 
               select(ann_agr_pland, prn_agr_pland, aglu_iji,
                      lu_shdi, aglu_frac_mn, lu_ta), 
             cex.cor = 1, cex.labels=1, cex=0.5, method = "pearson")
